The development of infants' responses to mispronunciations: A Meta-Analysis

### 2020-07-02 VonHolzenBergmann_MPMetaAnalysis.Rmd
wc correction factor removed

Our power analysis revealed that mispronunciation sensitivity studies typically underpowered, with `r ptt_power`% power and would need to increase their sample from an average of `r median_sample` to `r round(ptt.est$n, 0)`more infants to achieve 80% power. While this number does not seem to differ dramatically from the observed sample sizes, the impact of the smaller sample sizes on power is thus substantial and should be kept in mind when planning future studies. Furthermore, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which by some estimates require four times the sample size to detect an effect of similar magnitude as the main effect for both ANOVA [@Fleiss1986] and mixed-effect-model [@Leon2009] analyses. We thus strongly advocate for a consideration of power and the reported effect sizes to test infants’ mispronunciation sensitivity and factors influencing this ability.

>>>>

Our power analysis revealed that mispronunciation sensitivity studies typically underpowered, with `r ptt_power`% power and would need to increase their sample from an average of `r median_sample` to `r round(ptt.est$n, 0)` more infants to achieve 80% power. While this number does not seem to differ dramatically from the observed sample sizes, the impact of the smaller sample sizes on power is thus substantial and should be kept in mind when planning future studies. Furthermore, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which by some estimates require four times the sample size to detect an effect of similar magnitude as the main effect for both ANOVA [@Fleiss1986] and mixed-effect-model [@Leon2009] analyses. We thus strongly advocate for a consideration of power and the reported effect sizes to test infants’ mispronunciation sensitivity and factors influencing this ability.

### 2020-07-02 VonHolzenBergmann_MPMetaAnalysis.tex
wc correction factor removed

Figure \ref{fig:FunnelCombo} shows the funnel plots for both correct pronunciations and mispronunciations (code adapted from Sakaluk, 2016). Funnel plot asymmetry was significant for both correct pronunciations (Kendall's \(\tau\) = 0.53, \emph{p} \textless{} .001) and mispronunciations (Kendall's \(\tau\) = 0.16, \emph{p} = 0.004). These results, quantifying the asymmetry in the funnel plots (Figure \ref{fig:FunnelCombo}), indicate bias in the literature. This is particularly evident for correct pronunciations, where larger effect sizes have greater variance (bottom right corner) and the more precise effect sizes (i.e.~smaller variance) tend to be smaller than expected (top left, outside the triangle).

@@

We first calculated the meta-analytic effect for infants' ability to identify objects when hearing correctly pronounced labels. The variance-weighted meta-analytic effect size Hedges' \emph{g} was 0.916 (SE = 0.122), a large effect, which was significantly different from zero (CI {[}0.676, 1.156{]}, \emph{p} \textless{} .001) with a CI lower bound of 0.68. We then calculated the meta-analytic effect for object identification in response to mispronounced words. In this case, the variance-weighted meta-analytic effect size was 0.249 (SE = 0.06), a small effect, which was also significantly different from zero (CI {[}0.132, 0.366{]}, \emph{p} \textless{} .001). When presented with a correct or mispronounced label, infants fixated the correct object.

@@

The above two analyses considered the data from mispronounced and correctly pronounced words separately. To evaluate mispronunciation sensitivity, we compared the effect size Hedges' \emph{g} for correct pronunciations with mispronunciations directly. To this end, we combined the two datasets. When condition was included (correct, mispronounced), the moderator test was significant (QM(1) = 103.408, \emph{p} \textless{} .001). The estimate for mispronunciation sensitivity was 0.608 (SE = 0.06), and infants' looking behavior across conditions was significantly different (CI {[}0.49, 0.725{]}, \emph{p} \textless{} .001). This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations, suggesting sensitivity to mispronunciations.

The estimated effect for mispronunciation sensitivity in this meta-analysis is 0.61, and the median sample size is 24 participants. If we were to assume that researchers assess mispronunciation sensitivity in a simple paired t-test, the resulting power is 54\%. In other words, only about half the studies should report a significant result even with a true population effect. Reversely, to achieve 80\% power, one would need to test 43 participants.

Heterogeneity was significant for both correctly pronounced (Q(103) = 625.63, \emph{p} \textless{} .001) and mispronounced words, (Q(146) = 462.51, \emph{p} \textless{} .001), as well as mispronunciation sensitivity, which included the moderator condition (QE(249) = 1,088.14, \emph{p} \textless{} .001). This indicated that the sample contains unexplained variance leading to significant difference between studies beyond what is to be expected based on random sampling error. In our moderator analysis we investigate possible sources of this variance.

@@

In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not. Age did not significantly modulate object identification in response to correctly pronounced (QM(1) = 0.558, \emph{p} = 0.455) or mispronounced words (QM(1) = 1.64, \emph{p} = 0.2). The lack of a significant modulation together with the small estimates for age (correct: \(\beta\) = 0.014, SE = 0.019, 95\% CI{[}-0.022, 0.05{]}, \emph{p} = 0.455; mispronunciation: \(\beta\) = 0.015, SE = 0.011, 95\% CI{[}-0.008, 0.037{]}, \emph{p} = 0.2) indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label. However, previous experimental studies ((e.g.~Fernald, Pinto, Swingley, Weinberg, \& McRoberts, 1998)) and a recent meta-analysis (Frank, Lewis, \& Macdonald, 2016) have found that children's speed and accuracy in recognition of correctly pronounced words increases with age. Perhaps older children are more likely to be tested on less-frequent, later learned words than younger children, which could lead to a lack of a relationship between age and target looks in response to correct pronunciations in the current meta-analysis.

We then examined the interaction between age and mispronunciation sensitivity (correct vs.~mispronounced words) in our whole dataset. The moderator test was significant (QM(3) = 106.158, \emph{p} \textless{} .001). The interaction between age and mispronunciation sensitivity, however, was not significant (\(\beta\) = 0.012, SE = 0.013, 95\% CI{[}-0.014, 0.039{]}, \emph{p} = 0.349). The small estimate, as well as inspection of Figure \ref{fig:PlotMPEffect}, suggests that as infants age, their mispronunciation sensitivity neither increases or decreases.

@@

Our power analysis revealed that mispronunciation sensitivity studies typically underpowered, with 54\% power and would need to increase their sample from an average of 24 to 43more infants to achieve 80\% power. While this number does not seem to differ dramatically from the observed sample sizes, the impact of the smaller sample sizes on power is thus substantial and should be kept in mind when planning future studies. Furthermore, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which by some estimates require four times the sample size to detect an effect of similar magnitude as the main effect for both ANOVA (Fleiss, 1986) and mixed-effect-model (Leon \& Heo, 2009) analyses. We thus strongly advocate for a consideration of power and the reported effect sizes to test infants' mispronunciation sensitivity and factors influencing this ability.

@@

\scriptsize{
\begin{longtable}{lllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:mod_table_finalize}Summary of the 5 moderator tests, including effect estimates for effects and critical interactions.}\\
\toprule
Moderator & Moderator Test & Interaction Terms & Hedges' *g* & SE & 95 CI & *p*-value\\
\midrule
Misp. size & QM(1) = 61.081, *p* < .001 &  & -0.406 & 0.052 & [-0.507, -0.304] & < .001\\
 & QM(3) = 143.617, *p* < .001 & Age & 0.009 & 0.006 & [-0.002, 0.02] & = 0.099\\ \midrule
Misp. position & QM(3) = 172.345, *p* < .001 & Condition & -0.126 & 0.064 & [-0.252, 0] & = 0.049\\
 & QM(7) = 175.856, *p* < .001 & Condition * Age & 0.022 & 0.018 & [-0.013, 0.057] & = 0.223\\ \midrule
Misp. type & QM(3) = 145.138, *p* < .001 & Condition & 0.056 & 0.079 & [-0.099, 0.211] & = 0.479\\
 & QM(7) = 153.795, *p* < .001 & Condition * Age & 0.044 & 0.018 & [0.008, 0.08] & = 0.016\\
 & QM(7) = 158.889, *p* < .001 & Condition * Language Family & -0.872 & 0.28 & [-1.421, -0.323] & = 0.002\\
 & QM(15) = 185.148, *p* < .001 & Condition * Language Family * Age & 0.331 & 0.078 & [0.178, 0.484] & < .001\\ \midrule
Distractor overlap & QM(3) = 48.101, *p* < .001 & Condition & 0.195 & 0.213 & [-0.223, 0.612] & = 0.36\\
 & QM(7) = 67.82, *p* < .001 & Condition * Age & 0.091 & 0.038 & [0.017, 0.166] & = 0.016\\ \midrule
Distractor familiarity & QM(3) = 104.058, *p* < .001 & Condition & 0.067 & 0.137 & [-0.203, 0.336] & = 0.628\\
 & QM(7) = 107.683, *p* < .001 & Condition * Age & -0.021 & 0.035 & [-0.09, 0.048] & = 0.547\\
\bottomrule
\end{longtable}
}
\end{lltable}

@@

When post-naming analysis window length and condition (correct pronunciation, mispronunciation) were included as moderators, the moderator test was significant (QM(3) = 236.958, \emph{p} \textless{} .001). The estimate for the interaction between post-naming analysis window and condition was small but significant (\(\beta\) = -0.262, SE = 0.059, 95\% CI{[}-0.377, -0.148{]}, \emph{p} \textless{} .001), showing that as the length of the post-naming analysis window increased, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) decreased. This relationship is plotted in Figure \ref{fig:PlotPostNameCondAge}a. When age was added as a moderator, the moderator test was significant (QM(7) = 247.322, \emph{p} \textless{} .001). The estimate for the three-way-interaction between condition, post-naming analysis window, and age was small, but significant (\(\beta\) = -0.04, SE = 0.014, 95\% CI{[}-0.068, -0.012{]}, \emph{p} = 0.006). As can be seen in Figure \ref{fig:PlotPostNameCondAge}b, when records were analyzed with a post-naming analysis window of 2000 ms or less (a limit we imposed for visualization purposes), mispronunciation sensitivity seems to increase with infant age. If the post-naming analysis window is greater than 2000 ms, however, there is no or a negative relation between mispronunciation sensitivity and age.

@@

When we included both condition and dependent variable as moderators, the moderator test was significant (QM(3) = 232.117, \emph{p} \textless{} .001). The estimate for the interaction between the type of dependent variable and condition was was significant (\(\beta\) = -0.184, SE = 0.093, 95\% CI{[}-0.365, -0.002{]}, \emph{p} = 0.047). As can be seen in @ref(fig:PlotWithinCondDV\_baseline), mispronunciation sensitivity was higher when the dependent variable reported was Post compared to when it was Baseline Corrected. When age was included as an additional moderator, the moderator test was significant (QM(7) = 238.595, \emph{p} \textless{} .001). However, the estimate for the interaction between dependent variable, condition, and age was not significant (\(\beta\) = -0.048, SE = 0.026, 95\% CI{[}-0.1, 0.003{]}, \emph{p} = 0.064).

>>>>

Figure \ref{fig:FunnelCombo} shows the funnel plots for both correct pronunciations and mispronunciations (code adapted from Sakaluk, 2016). Funnel plot asymmetry was significant for both correct pronunciations (Kendall's \(\tau\) = 0.52, \emph{p} \textless{} .001) and mispronunciations (Kendall's \(\tau\) = 0.16, \emph{p} = 0.005). These results, quantifying the asymmetry in the funnel plots (Figure \ref{fig:FunnelCombo}), indicate bias in the literature. This is particularly evident for correct pronunciations, where larger effect sizes have greater variance (bottom right corner) and the more precise effect sizes (i.e.~smaller variance) tend to be smaller than expected (top left, outside the triangle).

@@

We first calculated the meta-analytic effect for infants' ability to identify objects when hearing correctly pronounced labels. The variance-weighted meta-analytic effect size Hedges' \emph{g} was 0.919 (SE = 0.122), a large effect, which was significantly different from zero (CI {[}0.679, 1.158{]}, \emph{p} \textless{} .001) with a CI lower bound of 0.68. We then calculated the meta-analytic effect for object identification in response to mispronounced words. In this case, the variance-weighted meta-analytic effect size was 0.251 (SE = 0.06), a small effect, which was also significantly different from zero (CI {[}0.134, 0.368{]}, \emph{p} \textless{} .001). When presented with a correct or mispronounced label, infants fixated the correct object.

@@

The above two analyses considered the data from mispronounced and correctly pronounced words separately. To evaluate mispronunciation sensitivity, we compared the effect size Hedges' \emph{g} for correct pronunciations with mispronunciations directly. To this end, we combined the two datasets. When condition was included (correct, mispronounced), the moderator test was significant (QM(1) = 102.114, \emph{p} \textless{} .001). The estimate for mispronunciation sensitivity was 0.606 (SE = 0.06), and infants' looking behavior across conditions was significantly different (CI {[}0.489, 0.724{]}, \emph{p} \textless{} .001). This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations, suggesting sensitivity to mispronunciations.

The estimated effect for mispronunciation sensitivity in this meta-analysis is 0.61, and the median sample size is 24 participants. If we were to assume that researchers assess mispronunciation sensitivity in a simple paired t-test, the resulting power is 54\%. In other words, only about half the studies should report a significant result even with a true population effect. Reversely, to achieve 80\% power, one would need to test 44 participants.

Heterogeneity was significant for both correctly pronounced (Q(103) = 626.38, \emph{p} \textless{} .001) and mispronounced words, (Q(146) = 466.45, \emph{p} \textless{} .001), as well as mispronunciation sensitivity, which included the moderator condition (QE(249) = 1,092.83, \emph{p} \textless{} .001). This indicated that the sample contains unexplained variance leading to significant difference between studies beyond what is to be expected based on random sampling error. In our moderator analysis we investigate possible sources of this variance.

@@

In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not. Age did not significantly modulate object identification in response to correctly pronounced (QM(1) = 0.537, \emph{p} = 0.464) or mispronounced words (QM(1) = 1.663, \emph{p} = 0.197). The lack of a significant modulation together with the small estimates for age (correct: \(\beta\) = 0.014, SE = 0.019, 95\% CI{[}-0.023, 0.05{]}, \emph{p} = 0.464; mispronunciation: \(\beta\) = 0.015, SE = 0.011, 95\% CI{[}-0.008, 0.037{]}, \emph{p} = 0.197) indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label. However, previous experimental studies ((e.g.~Fernald, Pinto, Swingley, Weinberg, \& McRoberts, 1998)) and a recent meta-analysis (Frank, Lewis, \& Macdonald, 2016) have found that children's speed and accuracy in recognition of correctly pronounced words increases with age. Perhaps older children are more likely to be tested on less-frequent, later learned words than younger children, which could lead to a lack of a relationship between age and target looks in response to correct pronunciations in the current meta-analysis.

We then examined the interaction between age and mispronunciation sensitivity (correct vs.~mispronounced words) in our whole dataset. The moderator test was significant (QM(3) = 104.837, \emph{p} \textless{} .001). The interaction between age and mispronunciation sensitivity, however, was not significant (\(\beta\) = 0.012, SE = 0.013, 95\% CI{[}-0.014, 0.038{]}, \emph{p} = 0.361). The small estimate, as well as inspection of Figure \ref{fig:PlotMPEffect}, suggests that as infants age, their mispronunciation sensitivity neither increases or decreases.

@@

Our power analysis revealed that mispronunciation sensitivity studies typically underpowered, with 54\% power and would need to increase their sample from an average of 24 to 44more infants to achieve 80\% power. While this number does not seem to differ dramatically from the observed sample sizes, the impact of the smaller sample sizes on power is thus substantial and should be kept in mind when planning future studies. Furthermore, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which by some estimates require four times the sample size to detect an effect of similar magnitude as the main effect for both ANOVA (Fleiss, 1986) and mixed-effect-model (Leon \& Heo, 2009) analyses. We thus strongly advocate for a consideration of power and the reported effect sizes to test infants' mispronunciation sensitivity and factors influencing this ability.

@@

\scriptsize{
\begin{longtable}{lllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:mod_table_finalize}Summary of the 5 moderator tests, including effect estimates for effects and critical interactions.}\\
\toprule
Moderator & Moderator Test & Interaction Terms & Hedges' *g* & SE & 95 CI & *p*-value\\
\midrule
Misp. size & QM(1) = 59.618, *p* < .001 &  & -0.403 & 0.052 & [-0.505, -0.301] & < .001\\
 & QM(3) = 140.626, *p* < .001 & Age & 0.009 & 0.006 & [-0.002, 0.02] & = 0.099\\ \midrule
Misp. position & QM(3) = 172.935, *p* < .001 & Condition & -0.146 & 0.064 & [-0.271, -0.02] & = 0.023\\
 & QM(7) = 176.208, *p* < .001 & Condition * Age & 0.018 & 0.018 & [-0.017, 0.053] & = 0.314\\ \midrule
Misp. type & QM(3) = 141.83, *p* < .001 & Condition & 0.043 & 0.079 & [-0.111, 0.198] & = 0.584\\
 & QM(7) = 149.507, *p* < .001 & Condition * Age & 0.041 & 0.018 & [0.005, 0.076] & = 0.026\\
 & QM(7) = 154.731, *p* < .001 & Condition * Language Family & -0.841 & 0.28 & [-1.39, -0.292] & = 0.003\\
 & QM(15) = 181.174, *p* < .001 & Condition * Language Family * Age & 0.344 & 0.078 & [0.191, 0.496] & < .001\\ \midrule
Distractor overlap & QM(3) = 48.551, *p* < .001 & Condition & 0.199 & 0.215 & [-0.222, 0.619] & = 0.354\\
 & QM(7) = 68.485, *p* < .001 & Condition * Age & 0.092 & 0.038 & [0.017, 0.166] & = 0.016\\ \midrule
Distractor familiarity & QM(3) = 102.487, *p* < .001 & Condition & 0.038 & 0.138 & [-0.233, 0.309] & = 0.783\\
 & QM(7) = 106.262, *p* < .001 & Condition * Age & -0.02 & 0.035 & [-0.089, 0.049] & = 0.574\\
\bottomrule
\end{longtable}
}
\end{lltable}

@@

When post-naming analysis window length and condition (correct pronunciation, mispronunciation) were included as moderators, the moderator test was significant (QM(3) = 237.055, \emph{p} \textless{} .001). The estimate for the interaction between post-naming analysis window and condition was small but significant (\(\beta\) = -0.268, SE = 0.059, 95\% CI{[}-0.383, -0.153{]}, \emph{p} \textless{} .001), showing that as the length of the post-naming analysis window increased, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) decreased. This relationship is plotted in Figure \ref{fig:PlotPostNameCondAge}a. When age was added as a moderator, the moderator test was significant (QM(7) = 247.485, \emph{p} \textless{} .001). The estimate for the three-way-interaction between condition, post-naming analysis window, and age was small, but significant (\(\beta\) = -0.04, SE = 0.014, 95\% CI{[}-0.068, -0.012{]}, \emph{p} = 0.006). As can be seen in Figure \ref{fig:PlotPostNameCondAge}b, when records were analyzed with a post-naming analysis window of 2000 ms or less (a limit we imposed for visualization purposes), mispronunciation sensitivity seems to increase with infant age. If the post-naming analysis window is greater than 2000 ms, however, there is no or a negative relation between mispronunciation sensitivity and age.

@@

When we included both condition and dependent variable as moderators, the moderator test was significant (QM(3) = 231.004, \emph{p} \textless{} .001). The estimate for the interaction between the type of dependent variable and condition was was significant (\(\beta\) = -0.185, SE = 0.093, 95\% CI{[}-0.366, -0.003{]}, \emph{p} = 0.046). As can be seen in @ref(fig:PlotWithinCondDV\_baseline), mispronunciation sensitivity was higher when the dependent variable reported was Post compared to when it was Baseline Corrected. When age was included as an additional moderator, the moderator test was significant (QM(7) = 237.51, \emph{p} \textless{} .001). However, the estimate for the interaction between dependent variable, condition, and age was not significant (\(\beta\) = -0.049, SE = 0.026, 95\% CI{[}-0.1, 0.002{]}, \emph{p} = 0.061).
